Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-26 analyses/2015_06_27_ResTime.Rmd

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/SimData.csv")  
sim.data <- subset(sim.data, motion == ' fluid ')
```

@@

@@

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}

png(filename = '~/GitHub/hydrobide/results/figs/ComparingResTimes.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

p1 <- ggplot(data=NULL, aes(x=h.tau, y=t.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="cyan") +
  labs(x= expression(tau), y="Residence Time") +
  labs(title="Tracers") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p2 <- ggplot(data=NULL, aes(x=h.tau, y=m.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="magenta") +
  labs(x= expression(tau), y=" ") +
  labs(title="Individuals") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p3 <- ggplot(data=NULL, aes(x=h.tau, y=r.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="chartreuse") +
  labs(x= expression(tau), y=" ") +
  labs(title="Resources") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 200)) +
  coord_fixed(ratio = 2.38) +
  theme_black()

multiplot(p1, p2, p3, cols=3)
dev.off()
```

@@

p1 <- ggplot(sim.data, aes(x=particle.tau, y=N, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Individuals") +
  labs(title="Total abundance") +
  guides(colour=FALSE) + 
  scale_x_log10(limits = c(10, 1000)) + 
  scale_y_log10(limits = c(100, 10000)) +
  coord_fixed(ratio = 1)

p2 <- ggplot(sim.data, aes(x=particle.tau, y=S, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Species") +
  labs(title="Numbers of species") +
  guides(colour=FALSE) +
  scale_x_log10(limits = c(10, 1000)) +
  coord_fixed(ratio = .0345)

@@

p1 <- ggplot(data=NULL, aes(x=xs, y=ys)) +
  geom_point(colour="magenta") +
  labs(x= expression(tau), y="Growth") +
  labs(title="Growth rate") +
  scale_x_log10(limits = c(20, 1000)) +
  coord_fixed(ratio = 4) +
  theme_black()

@@

p2 <- ggplot(data=NULL, aes(x=h.tau, y=maint)) +
  geom_point(colour="cyan") +
  labs(x= expression(tau), y="Maintenance") +
  labs(title="Maintenance") +
  scale_x_log10(limits = c(20, 1000)) +
  scale_y_log10() +
  coord_fixed(ratio = .5) +
  theme_black()

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Loading simulated RADs and species lists

rad.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/RADs.csv", header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)
rad.list[is.na(rad.list)] <- 0

species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/Species.csv", header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)), as.is = TRUE, skipNul = TRUE, fill = TRUE)
species.list[is.na(species.list)] <- -1
```

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_August/12_Aug/SimData.csv")  
#sim.data <- subset(sim.data, motion == ' random_walk ')
```

@@

N <- sim.data$N
S <- sim.data$S
e.var <- sim.data$e.var
e.simp <- sim.data$simpson.e
avg.ab <- N/S
Skew <-sim.data$skew
Nmax <- sim.data$N.max
SimpD <- sim.data$SD
Whittaker.turnover <- sim.data$species.turnover

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Loading files with plotting and diversity functions
source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")
source("~/GitHub/hydrobide/tools/Rbin/metrics.R")
```

@@

@@

sim.data$N[sim.data$N<=0] <- 1
sim.data$N[sim.data$S<=0] <- 1

p1 <- ggplot(sim.data, aes(x=h.tau, y=N, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Individuals") +
  labs(title="Total abundance") +
  guides(colour=FALSE) + 
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = .48)

p2 <- ggplot(sim.data, aes(x=h.tau, y=S, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Number of species") +
  labs(title="Species richness") +
  guides(colour=FALSE) +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 0.8)

## We hypothesized that the realtionship species evenness (E) to residence time would be U-shaped, and that the relationship of species turnover (B) to residence time would be L-shaped.

png(filename = '~/GitHub/hydrobide/results/figs/EandB_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=e.var, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Evar") +
  labs(title="Evenness") +
  guides(colour=FALSE) + 
  scale_x_log10() + 
  coord_fixed(ratio = 1.8)

p2 <- ggplot(sim.data, aes(x=h.tau, y=Whittaker.turnover, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Whittaker's") +
  labs(title="Species turnover") +
  guides(colour=FALSE) +
  scale_x_log10() +
  coord_fixed(ratio = 2.0)

@@

p1 <- ggplot(data=NULL, aes(x=xs, y=ys)) +
  geom_point(colour="magenta") +
  labs(x= expression(tau), y="Growth") +
  labs(title="Growth rate") +
  scale_x_log10() +
  coord_fixed(ratio = 5.3) +
  theme_black()

@@

p2 <- ggplot(data=NULL, aes(x=h.tau, y=maint)) +
  geom_point(colour="cyan") +
  labs(x= expression(tau), y="Maintenance") +
  labs(title="Maintenance") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 0.34) +
  theme_black()

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}
num.sims <- max(sim.data$sim) + 1

i <- 0
while (i < num.sims){

  sp.sub <- subset(sim.data$species.list, sim == i)
  sp.beta <- c()
  j <- 2
  while(j <= length(sp.sub)){
    print(j)
    w.beta <- sp.turnover(sp.sub[j], sp.sub[j-1])
    sp.beta <- c(sp.beta, w.beta)
    }
    j <- j+1
    }
  i <- i+1
  print(sp.beta)
  }
```
